Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-01-09 paper2.qmd
section:appendix; process:write

<!-- 2. What are the advantages of SCMs and DAGs? -->
SCMs and DAGs offer three key advantages for modeling causal structures. First, they enable researchers to represent causal relations in a non-parametric and fully interactive manner. This feature allows for feasible ACE identification strategies without specifying the data type or the nature of the functional dependence among variables [@Morgan_et_al_2014]. Second, regardless of complexity, they can represent a wide range of causal structures using only five fundamental building blocks [@Neal_2020; @McElreath_2020]. This feature allows researchers to decompose complex structures, facilitating their analysis by focusing on the causal assumptions associated with each building block [@McElreath_2020]. Finally, they help to formalize (causal) theoretical models into (probabilistic) statistical models for identification purposes [@McElreath_2020] [@McElreath_2020].

@@

Plausible causal structure of the example.
:::

@@

<!-- 1. But what does the building blocks mean? -->
<!-- [The advantages of SCMs and DAGs to identify causal quantities are realized after researchers examine the causal and probabilistic assumptions underlying these building blocks.]{style="color:red;"} -->

>>>>

<!-- 2. What are the advantages of SCMs and DAGs? -->
SCMs and DAGs offer two key advantages for modeling causal structures. First, they enable researchers to represent causal relations in a non-parametric and fully interactive manner. This feature allows for feasible ACE identification strategies without specifying the data type or the nature of the functional dependence among variables [@Morgan_et_al_2014]. Second, regardless of complexity, they can represent a wide range of causal structures using only five fundamental building blocks [@Neal_2020; @McElreath_2020]. This feature allows researchers to decompose complex structures, facilitating their analysis by focusing on the causal assumptions associated with each building block [@McElreath_2020].

@@

Plausible causal structure for the example.
:::

@@

<!-- 1. But what does the building blocks mean? -->
<!-- Ultimately, SCMs and DAGS help to formalize (causal) theoretical models into (probabilistic) statistical models for identification purposes [@McElreath_2020]. -->

<!-- [The advantages of SCMs and DAGs to identify causal quantities are realized after researchers examine the causal and probabilistic assumptions underlying these building blocks.]{style="color:red;"} -->
